---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RAMEN

<!-- badges: start -->
<!-- badges: end -->

Regional Association of Methylation variability with genotype and ENvironment (RAMEN) is an R package whose goal is to identify Variable Methylated Regions (VMRs) in a microarray methylation data set and, using Genotype (G) and Environmental (E) data, then to identify the independent or joint model (G, E, G + E or GxE) that best explains its variability.

## Installation

You can install the development version of RAMEN from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ErickNavarroD/RAMEN")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(RAMEN)
## basic example code
```

